OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-06-08 main.tex
Added funding

This work was supported by the Spanish Ministry of Economy and
Competitiveness, ‘Centro de Excelencia Severo Ochoa 2013-2017’,
SEV-2012-0208 and ERC Synergy Grant 609989. R.S. was supported by an EMBO Long-term
Fellowship (ALTF 1201-2014) and a Marie Curie Individual Fellowship (H2020-MSCA-IF-2014).

>>>>

This work was partially supported by the Spanish Ministry of Economy and
Competitiveness 'Centro de Excelencia Severo Ochoa 2013-2017' (SEV-2012-0208)
and ACER to CRG. R.S. was supported by an EMBO Long-term
Fellowship (ALTF 1201-2014) and a Marie Curie Individual Fellowship
(H2020-MSCA-IF-2014). We received funding from the European Research Council under
the European Union's Seventh Framework Programme (FP7/2007-2013)/ERC Synergy
grant agreement 609989 (4DGenome). The content of this manuscript reflects only
the author’s views and the Union is not liable for any use that may be made of
the information contained therein.
